---
title: "BigDataProject"
format: html
editor: visual
---

# Big Data Project

## Table of Contents

## Introduction

This text is to be replaced by the actual introduction text.

## Methodology

This text is to be replaced by the actual introduction text. We are going to use KNN for the classification problem, include simple example/description.

Briefly description of the steps we will make: 1. Presentation of the data. 2. Data processing. 3. Model validation/testing.

```{r}
library(ggplot2)
```

## Results

Text with the results.

## Conclusions

Text with the conclusions.

## Annex

This section will contain whatever we consider should be here.

### Scripts

Text with the full scripts. We will also send the scripts (R script file).

### Something else we can add

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
